Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd

```{r eval=FALSE}
summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), 
            num_faces_center = sum(num_faces_center), 
            num_hands = sum(num_hands), 
            num_hands_center = sum(num_hands_center), 
            num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect,
         prop_faces_center = num_faces_center / num_detect, 
          prop_hands_center = num_hands_center / num_detect)

>>>>

```{r eval=T}
summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), 
            num_faces_center = sum(num_faces_center), 
            num_hands = sum(num_hands), 
            num_hands_center = sum(num_hands_center), 
            num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect,
         prop_faces_center = num_faces_center / num_detect, 
          prop_hands_center = num_hands_center / num_detect)
